Conditional selectivity for Hexastores

### 2011-07-20 conditional/trunk/selectivity-hexastore.tex
single triple patterns
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@14 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{abstract}
In this paper we see how the common assumption of independence of the
selectivity of RDF terms can be abandoned. We shall also find it
instructive to explore how selectivity can be determined exactly when
a SPARQL query is executed on a Hexastore triple store
\cite{Weiss:2008:HSI:1453856.1453965}. Finally, we will suggest
further directions for selectivity estimation in the conditional
regime.

>>>>

\begin{abstract}
This paper explores selectivity estimation for single triple patterns
in SPARQL queries.
In this paper we see how the common assumption of independence of the
selectivity of RDF terms can be abandoned. We shall also find it
instructive to explore how selectivity can be determined exactly when
a SPARQL query is executed on a Hexastore triple store
\cite{Weiss:2008:HSI:1453856.1453965}. Finally, we will suggest
further directions for selectivity estimation in the conditional
regime.
